Commutative character sheaves and geometric types for supercuspidal representations

### 2017-08-04 Geometric types.tex
Working on section 4

For connected, commutative groups, the standard method for geometrizing a character $\chi$ is to use the Lang isogeny $L : G \to G$, defined by $L(x) = x^{-1}\Frob{G}(x)$.  Then the pushforward $L_! (\EE)_G$ of the constant sheaf decomposes into a direct sum of rank $1$ local systems according to characters of the automorphism group $G(k)$ of the cover $L$.

>>>>

For connected, commutative groups, the standard method for geometrizing a character $\chi$ is to use the Lang isogeny $L : G \to G$, defined by $L(y) = y^{-1}\Frob{G}(y)$.  The pushforward $L_! (\EE)_G$ of the constant sheaf decomposes into a direct sum of rank $1$ local systems according to characters of the automorphism group $G(k)$ of the cover $L$.

If $G$ is nonabelian or disconnected, a similar strategy sometimes succeeds in geometrizing characters $\chi : G(k) \to \EEx$.
Suppose that $G(k) \subset \image(L)$ (which will hold if $G$ is connected).  Then we may associate to each $\chi$ a function $\tilde{\chi}$ as follows.
If $x \in G(k)$, write $x = L(y) = y^{-1}\Frob{G}(y)$ and define $\tilde{\chi}(x) = \chi(\Frob{G}(y) y^{-1})$.
Note that $\tilde{\chi}$ is well defined since changing to $y$ to $gy$ for $g \in G(k)$ has the
effect of conjugating $\Frob{G}(y) y^{-1}$ by $g$, which has no effect on the value of $\chi(\Frob{G}(y) y^{-1})$.
Our second assumption required to geometrize $\chi$ is that $\tilde{\chi}$ is also a character.
